State of the Practice for Lattice Boltzmann Method Software

### 2022-02-26 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Minor edits to Section 9.1

As the LBM developers illustrate, design for changes is accomplished by first
identifying likely changes, either implicitly or explicitly, and second by
hiding those likely changes behind well-defined module interfaces.

>>>>

As the LBM developers illustrate, design for changes is accomplished by first
identifying likely changes, either implicitly or explicitly, and second by
hiding each likely change behind a well-defined module interface.  Although it
is unclear whether the developers are aware of Parnas's work, the approach
mirrors his recommendations \citep{Parns1972a}.
